### 2018-07-17 relatedwork.tex
fix up for ISSRE camera ready

The most closely related work is that of Chen et. al \cite{PLDI13}.  We use two of the same compiler data sets, and both apply the FPF \cite{Gonzalez} algorithm.  The distance metrics used with FPF in the previous work, however, were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper uses the FPF approach in the context of a more causal comparison of program executions that applies in theory to any executions, not just failing test cases, and introduces a novel fault localization.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  Chen et. al \cite{PLDI13} provide an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.  The work of Groce et al. \cite{OneTest} provides an alternative approach to fault identification, based on term rewriting to normalize failures.  However, this approach is not currently applicable to compiler fuzzing, as it only support tests that are sequences of method calls.

>>>>

The most closely related work is that of Chen et. al \cite{PLDI13}, whose FPF \cite{Gonzalez} algorithm and benchmark we use.  We extend their work with a better, and more universal distance metric, as well as an approach to fault localization in addition to fuzzer taming.Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  Chen et. al \cite{PLDI13} provide an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults \cite{Jones07}.  The work of Groce et al. \cite{OneTest} provides an alternative approach to fault identification, based on term rewriting to normalize failures, but is not currently applicable to compiler fuzzing, as it only supports tests that are sequences of method calls in Python \cite{ISSTA15,tstlsttt}.
